### 2022-07-12 ms/ms.rmd
Writing
Adding programmed version numbers and correct some errors

We extracted means, standard deviations and sample sizes for physiological rates at the two test temperatures. If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question. We extracted these data from text, tables or figures of a given paper. Data were extracted from figures using the R package *metaDigitise* [@pick2019]. We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied. For studies that did not provide latitude and longitude for the population, we searched for similar studies by the lab group to identify where the population was likely to have been sourced or derived from when needed. If the population was derived from the wild, we recorded the nearest latitude and longitude of the population to the field collection site. If the animals had been sourced from a commercial supplier, we took the latitude and longitude of the supplier that the paper identified the animals to have originated from. When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.

@@

#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
Using the mean, standard deviation and sample size for all acute and aclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates. For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator. As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.

@@

We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates. These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimitization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015]. We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates. Physiological rates measures varied widely across the studies but could generally be groups into discrete trait categories [@Seebacher2015]. As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of

### *Meta-Analysis*

@Guangchuang2017
\
### *Sensitivity Analyses*
### *Publication Bias*

>>>>

We extracted means, standard deviations and sample sizes for physiological rates at the two test temperatures. If there were more than two test temperatures, we choose only the test temperatures that fell within the most likely natural range of temperatures experienced by the species in question. We extracted these data from text, tables or figures of a given paper. Data were extracted from figures using the R package *metaDigitise* [@Pick2019]. We also recorded the phylum, class, order, genus and species under study and the latitude and longitude of the population that was being studied. For studies that did not provide latitude and longitude for the population, we searched for similar studies by the lab group to identify where the population was likely to have been sourced or derived from when needed. If the population was derived from the wild, we recorded the nearest latitude and longitude of the population to the field collection site. If the animals had been sourced from a commercial supplier, we took the latitude and longitude of the supplier that the paper identified the animals to have originated from. When it was not possible to find latitude and longitude using these methods, we looked up the distribution of the species in question and took the latitude and longitude of the centroid of the species' distributional range.

@@

#### *Calculating acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates*
Using the mean, standard deviation and sample size for all acute and acclimation treatments of studies in our databases we derived acute and acclimation $lnRR_{Q_{10}}$, $lnVR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ estimates. For all effect sizes the higher acute or acclimation temperature was in the numerator and the lower of the two temperatures in the denominator. As such, positive effect sizes suggest that the mean or variance is larger at the higher of the two temperatures, standardized to 10&deg;C.

@@

We recorded or derived a series of moderator variables from each study that are expected to have an impact on our effect size estimates. These included the duration of acclimation in days and acclimation type ("acclimation" or "acclimatization") given that acclimation responses are expected to depend both on how long chronic temperature exposure occurs (longer exposure = better acclimation response) and whether exposure took place in the wild ("acclimatized") or lab ("acclimated") [@Seebacher2015]. We also recorded if the sample of animals were derived from captive or wild stocks, the life-history stage of the animals used ("adult" or "juvenile") and the habitat type ("freshwater", "marine" or "terrestrial") given that @Seebacher2015 show that these factors can impact $Q_{10}$ estimates. Physiological rate measures varied widely across the studies but could generally be grouped into discrete trait categories [@Seebacher2015]. As such, using the detailed information on the trait type and its associated units from a given study we categorized each effect size into one of

### *Meta-Analysis*
We analysed our data using Bayesian multilevel meta-analytic and meta-regression models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan]. 
@Guangchuang2017

### *Sensitivity Analyses*
### *Publication Bias*
